### 2014-03-07 docs/related-work.tex
Typo.
Remove redundant description of active probing.

To protect the relays from being detected and blocked, a school of research
tries to use covert channels for the communication with relays.
FreeWave~\cite{freewave} encodes data into audio streams and use the Skype P2P
network to communicate with the proxy located outside the censored domain, which
is essentially another Skype client that decodes the stream. The proxy then
forward the traffic to the true destination. CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channel. It assumes the existence of a
low-bandwidth indirect channel that is immune from censorship. It uses this
channel for send requests (URLs) to the proxy while sending dummy requests to a
dummy host. The proxy then fetches the web content and spoofs the dummy host's
IP address to deliver the content back. A technique known as OSS~\cite{oss}, for
``online scanning service,'' closely resembles ours in important ways. It uses a
third-party web service as a conduit to carry traffic, encoded either in a URL
or in an HTTP body. Because web services cannot in general be assumed to
reproduce a web server's response exactly (a translation service, for example,
returns a response after translating it to another language), OSS does not use
response bodies to carry data, instead requiring the relay to initiate a
reflected request back to the client. OSS also does not claim that any one
service is difficult to block, rather that there are many web services that can
be used. The main ways in which this work differs is that we effectively control
the OSS: we can count on response bodies being preserved and so use them to send
downstream data; and we put the OSS on infrastructure that is expensive to
block.\\

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. In addition, their
experiments show that the Great Firewall of China actively scans for Tor bridges
and block them. Therefore, another school of research focuses on obfuscation
techniques for hiding protocol patterns. One technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. Another is
to resemble a protocol that is explicitly allowed; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream. A examples
of such a transport is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
content of its payloads, but takes additional steps to obscure its signature of
packet lengths and timing, and is designed to resist active scanning for proxies
(the proxy server says nothing until the client proves knowledge of a shared
secret). Another path to obfsucation is the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
to hide the upstream channel.\\

>>>>

To protect the relays from being detected and blocked, a school of research
tries to use covert channels for the communication with relays.
FreeWave~\cite{freewave} encodes data into audio streams and use the Skype P2P
network to communicate with the proxy located outside the censored domain, which
is essentially another Skype client that decodes the stream. The proxy then
forward the traffic to the true destination. CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channel. It assumes the existence of a
low-bandwidth indirect channel that is immune from censorship. It uses this
channel for sending requests (URLs) to the proxy while sending dummy requests to a
dummy host. The proxy then fetches the web content and spoofs the dummy host's
IP address to deliver the content back. A technique known as OSS~\cite{oss}, for
``online scanning service,'' closely resembles ours in important ways. It uses a
third-party web service as a conduit to carry traffic, encoded either in a URL
or in an HTTP body. Because web services cannot in general be assumed to
reproduce a web server's response exactly (a translation service, for example,
returns a response after translating it to another language), OSS does not use
response bodies to carry data, instead requiring the relay to initiate a
reflected request back to the client. OSS also does not claim that any one
service is difficult to block, rather that there are many web services that can
be used. The main ways in which this work differs is that we effectively control
the OSS: we can count on response bodies being preserved and so use them to send
downstream data; and we put the OSS on infrastructure that is expensive to
block.\\

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another school of research focuses on obfuscation
techniques for hiding protocol patterns. One technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. Another is
to resemble a protocol that is explicitly allowed; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream. A examples
of such a transport is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
content of its payloads, but takes additional steps to obscure its signature of
packet lengths and timing, and is designed to resist active scanning for proxies
(the proxy server says nothing until the client proves knowledge of a shared
secret). Another path to obfsucation is the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
to hide the upstream channel.\\
